Contribution Title\thanks{Supported by organization x.}

### 2019-12-03 sections/evaluation.tex
address a reproducibility issue in comment

>>>>

\nf{Benchmark results from running $\expSAT$ are harder to produce due to the randomness caused by the solver's strategy for selecting branching heuristics: the solver runs 2500s with LBR and the remaining 2500s with VSIDS. This is problematic for reproducing results because two runs of the same solver can be in different states at 2500s mark, and switching heuristics at different states will cause further divergence. The divergence can be quiet impactful (+- 2 instances at most for i-uip-active). For reproducible benchmark results, should we turn off the 2500s heuristic switching? Should we add a new section for the reproducible result? or remove the existing ones?}
